High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-10 notebooks/mnist.qmd
why did my brain decide to come up with this last night and not 3 months ago :fire: :cry:

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
    model_dict=model_dict,
    wide::Bool = false,
    img_height::Int = img_height,
    plot_factual::Bool = false,
    generator::Union{Nothing,CounterfactualExplanations.AbstractGenerator}=nothing,
    test_data::Bool = false,
    kwrgs...,
)

@@

    if isnothing(generator)
        # Generate counterfactuals using ECCCo generator:
        generator = ECCCoGenerator(
            λ=λ, 
            temp=temp, 
            opt=opt,
            use_class_loss=use_class_loss,
            nsamples=10,
            nmin=10,
        )
    end

@@

>>>>

```{julia}
function plot_mnist(ce; size=(img_height, img_height), kwrgs...)
    x = CounterfactualExplanations.counterfactual(ce)
    phat = target_probs(ce)
    plt = Plots.plot(
        convert2image(MNIST, reshape(x,28,28));
        axis=([], false), 
        size=size,
        kwrgs...,
    )
end

function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
    model_dict=model_dict,
    wide::Bool = false,
    img_height::Int = img_height,
    plot_factual::Bool = false,
    generator::Union{Nothing,CounterfactualExplanations.AbstractGenerator}=nothing,
    test_data::Bool = false,
    use_energy_delta::Bool = false,
    kwrgs...,
)

@@

    if isnothing(generator)
        # Generate counterfactuals using ECCCo generator:
        generator = ECCCoGenerator(
            λ=λ, 
            temp=temp, 
            opt=opt,
            use_class_loss=use_class_loss,
            nsamples=10,
            nmin=10,
            use_energy_delta=use_energy_delta,
        )
    end

@@

#### Energy Delta (not in paper)

```{julia}
λ_delta = [0.1,0.1,2.5]
λ = [0.1,0.25,0.25]
plts = []
for i in 0:9
    plt, _, _ = _plot_eccco_mnist(x_factual, i; λ = λ, plot_title="Distance")
    plt_delta, _, _ = _plot_eccco_mnist(x_factual, i; λ = λ_delta, use_energy_delta=true, plot_title="Energy Delta")
    plt = Plots.plot(plt, plt_delta; size=(img_height*2,img_height), layout=(1,2))
    display(plt)
    push!(plts, plt)
end
```
